### 2015-04-22 doc/notebook/2015-02-26_Bacterial_data_acquisition.Rmd
Update code to put mothur files into data/mothur/

```{r screen_data, engine="bash"}
mothur "#set.current(processors=8);
        set.dir(input=data/raw, output=data/process)
        screen.seqs(fasta=bacteria.fasta, taxonomy=bacteria.tax, start=2000, end=13000, maxambig=2, minlength=1200);"
```

@@

```{r}
bad_accnos_data <- read.table(file="data/process/bacteria.bad.accnos", col.names=c("name.accnos", "reason"))
bad_accnos <- bad_accnos_data$name.accnos
metadata_good <- metadata[-c(bad_accnos),]
write.table(metadata_good, file="data/process/all_bacteria.good.metadata", quote=F, sep="\t")
```

@@

spread_sheet <- read.xlsx("data/raw/BacterialSSUMetadata.xlsx", sheet=1, startRow=1, colNames=TRUE)
bad_accnos_data <- read.table(file="data/process/single_cell.bacteria.bad.accnos", col.names=c("name.accnos", "reason"))
bad_accnos <- bad_accnos_data$name.accnos
spread_sheet_good <- spread_sheet[-c(bad_accnos),]

write.table(spread_sheet_good, file="data/process/all_bacteria.good.metadata", quote=F, sep="\t", col.names=F, append=T)
```

>>>>

```{r screen_data, engine="bash"}
mothur "#set.current(processors=8);
        set.dir(input=data/raw, output=data/mothur)
        screen.seqs(fasta=bacteria.fasta, taxonomy=bacteria.tax, start=2000, end=13000, maxambig=2, minlength=1200);"
```

@@

```{r}
bad_accnos_data <- read.table(file="data/mothur/bacteria.bad.accnos", col.names=c("name.accnos", "reason"))
bad_accnos <- bad_accnos_data$name.accnos
metadata_good <- metadata[-c(bad_accnos),]
write.table(metadata_good, file="data/mothur/all_bacteria.good.metadata", quote=F, sep="\t")
```

@@

spread_sheet <- read.xlsx("data/raw/BacterialSSUMetadata.xlsx", sheet=1, startRow=1, colNames=TRUE)
bad_accnos_data <- read.table(file="data/mothur/single_cell.bacteria.bad.accnos", col.names=c("name.accnos", "reason"))
bad_accnos <- bad_accnos_data$name.accnos
spread_sheet_good <- spread_sheet[-c(bad_accnos),]

write.table(spread_sheet_good, file="data/mothur/all_bacteria.good.metadata", quote=F, sep="\t", col.names=F, append=T)
```

### 2015-04-22 doc/notebook/2015-03-13_Archaeal_data_acquisition.Rmd
Update code to put mothur files into data/mothur/

spread_sheet <- read.xlsx("data/raw/ArchaealSSUMetadata.xlsx", sheet=1, startRow=1, colNames=TRUE)
bad_accnos_data <- read.table(file="data/process/single_cell.archaea.bad.accnos", col.names=c("name.accnos", "reason"))
bad_accnos <- bad_accnos_data$name.accnos
spread_sheet_good <- spread_sheet[-c(bad_accnos),]

write.table(spread_sheet_good, file="data/process/all_archaea.good.metadata", quote=F, sep="\t", col.names=F, append=T)
```

>>>>

spread_sheet <- read.xlsx("data/raw/ArchaealSSUMetadata.xlsx", sheet=1, startRow=1, colNames=TRUE)
bad_accnos_data <- read.table(file="data/mothur/single_cell.archaea.bad.accnos", col.names=c("name.accnos", "reason"))
bad_accnos <- bad_accnos_data$name.accnos
spread_sheet_good <- spread_sheet[-c(bad_accnos),]

write.table(spread_sheet_good, file="data/mothur/all_archaea.good.metadata", quote=F, sep="\t", col.names=F, append=T)
```
